Highly Available Transactions: Virtues and Limitations

### 2013-04-29 writeup/evaluation.tex
small nits

\vspace{.5em}\noindent\textit{Implementation.} Our prototype database
is a partially replicated (hash-based, partitioned) key-value backed
by LevelDB and implemented in Java using Apache Thrift. Our prototype
currently supports eventual consistency (via simple anti-entropy) and
HAT RU, RC, and TA guarantees (as described in
Section~\ref{sec:hats}). It also supports non-HAT operation whereby
all operations for a given key are routed to a (randomly) designated
\textit{master} replica for each key (i.e., PNUTS~\cite{pnuts}) as
well as distributed two-phase locking. Servers are durable: they
synchronously write to LevelDB before responding to client requests,
while pending writes in TA are sent to a write-ahead log, which is
synchronously flushed to disk.

\vspace{.5em}\noindent\textit{Configuration.} We deploy the database
in \textit{clusters}---sets of database servers that contain a single,
fully replicated copy of the data---typically across datacenters,
sticking all clients within a datacenter to their respective cluster
(trivially providing read-your-writes and monotonic reads
guarantees). By default, we use 5 Amazon EC2 \texttt{m1.xlarge}
instances as servers in each cluster. For our workload, we link our
client library to the YCSB benchmark~\cite{ycsb}, grouping every eight
YCSB operations from the default workload (50\% reads, 50\% writes) to
form a transaction. We increase the number of keys in the workload
from the default $1,000$ to $100,000$ with uniform random key access,
keeping the default value size of $1KB$, and running YCSB for 180
seconds per configuration.

>>>>

\vspace{.5em}\noindent\textit{Implementation.} Our prototype database
is a partially replicated (hash-based, partitioned) key-value backed
by LevelDB and implemented in Java using Apache Thrift. It currently
supports eventual consistency (last-writer-wins RU, via simple
anti-entropy) and HAT RC and TA guarantees (as described in
Section~\ref{sec:hats}). It also supports non-HAT operation whereby
all operations for a given key are routed to a (randomly) designated
\textit{master} replica for each key (i.e., PNUTS~\cite{pnuts}) as
well as distributed two-phase locking. Servers are durable: they
synchronously write to LevelDB before responding to client requests,
while pending writes in TA are sent to a write-ahead log, which is
synchronously flushed to disk.

\vspace{.5em}\noindent\textit{Configuration.} We deploy the database
in \textit{clusters}---disjoint sets of database servers that each
contain a single, fully replicated copy of the data---typically across
datacenters, sticking all clients within a datacenter to their
respective cluster (trivially providing read-your-writes and monotonic
reads guarantees). By default, we use 5 Amazon EC2 \texttt{m1.xlarge}
instances as servers in each cluster. For our workload, we link our
client library to the YCSB benchmark~\cite{ycsb}, grouping every eight
YCSB operations from the default workload (50\% reads, 50\% writes) to
form a transaction. We increase the number of keys in the workload
from the default $1,000$ to $100,000$ with uniform random key access,
keeping the default value size of $1KB$, and running YCSB for 180
seconds per configuration.

### 2013-04-29 writeup/hat-analysis.tex
small nits

\begin{table}[t!]
\begin{tabular}{| c | p{6cm} | }\hline
HA & Transactional Atomicity (TA), Read Uncommitted (RU), Read
Committed (RC), Item Cut Isolation (I-CI), Predicate Cut Isolation
(P-CI), Monotonic Reads (MR), Monotonic Writes (MW), Writes Follow
Reads (WFR)\\\hline Sticky-HA & Read Your Writes (RYW), PRAM,
Causal\\\hline Unavailable & Cursor Stability (CS)\lostupdate,
Snapshot Isolation (SI)\lostupdate, Repeatable Read
(RR)\lostupdate\rwskew, One-Copy Serializability
(1SR)\lostupdate\rwskew, Recency\linearizable, Safe\linearizable,
Regular\linearizable, Linearizability\linearizable, Strong
1SR\lostupdate\rwskew\linearizable \\\hline
\end{tabular}
\caption{Summary of highly available, sticky highly available, and
  unavailable models considered in this paper. Unavailable models are
  labeled by cause of unavailability: preventing lost
  update\lostupdate, preventing write skew\rwskew, and requiring
  recency guarantees\linearizable.}\vspace{-1.5em}
\label{table:hatcompared}
\end{table}

>>>>

\begin{table}[t!]
\begin{tabular}{| c | p{6cm} | }\hline
HA & Transactional Atomicity (TA), Read Uncommitted (RU), Read
Committed (RC), Item Cut Isolation (I-CI), Predicate Cut Isolation
(P-CI), Monotonic Reads (MR), Monotonic Writes (MW), Writes Follow
Reads (WFR)\\\hline Sticky-HA & Read Your Writes (RYW), PRAM,
Causal\\\hline Unavailable & Cursor Stability (CS)\lostupdate,
Snapshot Isolation (SI)\lostupdate, Repeatable Read
(RR)\lostupdate\rwskew, One-Copy Serializability
(1SR)\lostupdate\rwskew, Recency\linearizable, Safe\linearizable,
Regular\linearizable, Linearizability\linearizable, Strong
1SR\lostupdate\rwskew\linearizable \\\hline
\end{tabular}
\caption{Summary of highly available, sticky highly available, and
  unavailable models considered in this paper. Unavailable models are
  labeled by cause of unavailability: preventing lost
  update\lostupdate, preventing write skew\rwskew, and requiring
  recency guarantees\linearizable.}\vspace{-.5em}
\label{table:hatcompared}
\end{table}
